Synthesising Concise Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-07-07 papers/termination/paper.tex
add thor to limitations

{\bf Limitations.} Our algorithm proves termination for transition systems
with finite state spaces.  The (non-)termination proofs take the form of
ranking functions and program invariants that are expressed in a
quantifier-free language.  This formalism is powerful enough to handle a
large fragment of C, but is not rich enough to analyse code that uses the
heap or unbounded arrays.  Also, we have not yet added support for recursion
to our encoding.

>>>>

{\bf Limitations.} Our algorithm proves termination for transition systems
with finite state spaces.  The (non-)termination proofs take the form of
ranking functions and program invariants that are expressed in a
quantifier-free language.  This formalism is powerful enough to handle a
large fragment of C, but is not rich enough to analyse code that uses 
unbounded arrays or the heap. Similar to other termination analyses \cite{DBLP:conf/tacas/CookSZ13}, we could attempt to alleviate the latter limitation by abstracting programs with heap to arithmetic ones \cite{DBLP:conf/popl/MagillTLT10}. Also, we have not yet added support for recursion
to our encoding.
